Title here

### 2020-07-08 analysis/paper/paper.Rmd
spectrum

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "",     # AMS required
                      out.extra = "",    # To force figure labels
                      echo = FALSE)      # Don't show R code

# This helps to use appendix figures.
appendcaption <- function (x, options) {
  `%n%` <- knitr:::`%n%`
  rw = options$resize.width
  rh = options$resize.height
  resize1 = resize2 = ""
  if (!is.null(rw) || !is.null(rh)) {
    resize1 = sprintf("\\resizebox{%s}{%s}{", rw %n% "!", 
                      rh %n% "!")
    resize2 = "} "
  }
  tikz = knitr:::is_tikz_dev(options)
  a = options$fig.align
  fig.cur = options$fig.cur %n% 1L
  fig.num = options$fig.num %n% 1L
  animate = options$fig.show == "animate"
  fig.ncol = options$fig.ncol %n% fig.num
  if (is.null(fig.sep <- options$fig.sep)) {
    fig.sep = character(fig.num)
    if (fig.ncol < fig.num) 
      fig.sep[seq(fig.ncol, fig.num - 1L, fig.ncol)] = "\\newline"
  }
  sep.cur = NULL
  if (!tikz && animate && fig.cur < fig.num) 
    return("")
  usesub = length(subcap <- options$fig.subcap) && fig.num > 
    1
  ai = options$fig.show != "hold"
  plot1 = ai || fig.cur <= 1L
  plot2 = ai || fig.cur == fig.num
  align1 = if (plot1) 
    switch(a, left = "\n\n", center = "\n\n{\\centering ", 
           right = "\n\n\\hfill{}", "\n")
  align2 = if (plot2) 
    switch(a, left = "\\hfill{}\n\n", center = "\n\n}\n\n", 
           right = "\n\n", "")
  cap = options$fig.cap
  appendix = !is.null(options$appendix)
  scap = options$fig.scap
  fig1 = fig2 = ""
  mcap = fig.num > 1L && options$fig.show == "asis" && !length(subcap)
  sub1 = sub2 = ""
  if (length(cap) && !is.na(cap)) {
    lab = paste0(options$fig.lp, options$label)
    if (plot1) {
      pos = options$fig.pos
      if (pos != "" && !grepl("^[[{]", pos)) 
        pos = sprintf("[%s]", pos)
      fig1 = sprintf("\\begin{%s}%s", options$fig.env, 
                     pos)
    }
    if (usesub) {
      sub1 = sprintf("\\subfloat[%s%s]{", subcap, knitr:::create_label(lab, 
                                                               fig.cur, latex = TRUE))
      sub2 = "}"
      sep.cur = fig.sep[fig.cur]
      if (is.na(sep.cur)) 
        sep.cur = NULL
    }
    if (plot2) {
      if (is.null(scap) && !grepl("[{].*?[:.;].*?[}]", 
                                  cap)) {
        scap = strsplit(cap, "[:.;]( |\\\\|$)")[[1L]][1L]
      }
      scap = if (is.null(scap) || is.na(scap)) 
        ""
      else sprintf("[%s]", scap)
      if (cap == "") {
        cap = ""
      } else if (appendix == TRUE) {
        cap = sprintf("\\appendcaption{%s}{%s}%s\n", options$label, cap, knitr:::create_label(lab, 
                                                                  if (mcap) 
                                                                    fig.cur, latex = TRUE))
      } else {
        cap = sprintf("\\caption%s{%s}%s\n", scap, cap, knitr:::create_label(lab, 
                                                                  if (mcap) 
                                                                    fig.cur, latex = TRUE))
      }
      fig2 = sprintf("%s\\end{%s}\n", cap, options$fig.env)
    }
  }
  else if (knitr:::pandoc_to(c("latex", "beamer"))) {
    align.env = switch(a, left = "flushleft", center = "center", 
                       right = "flushright")
    align1 = if (plot1) 
      if (a == "default") 
        "\n"
    else sprintf("\n\n\\begin{%s}", align.env)
    align2 = if (plot2) 
      if (a == "default") 
        ""
    else sprintf("\\end{%s}\n\n", align.env)
  }
  ow = options$out.width
  if (animate && identical(ow, "\\maxwidth")) 
    ow = NULL
  if (is.numeric(ow)) 
    ow = paste0(ow, "px")
  size = paste(c(sprintf("width=%s", ow), sprintf("height=%s", 
                                                  options$out.height), options$out.extra), collapse = ",")
  paste0(fig1, align1, sub1, resize1, if (tikz) {
    sprintf("\\input{%s}", x)
  }
  else if (animate) {
    aniopts = options$aniopts
    aniopts = if (is.na(aniopts)) 
      NULL
    else gsub(";", ",", aniopts)
    size = paste(c(size, sprintf("%s", aniopts)), collapse = ",")
    if (nzchar(size)) 
      size = sprintf("[%s]", size)
    sprintf("\\animategraphics%s{%s}{%s}{%s}{%s}", size, 
            1/options$interval, sub(sprintf("%d$", fig.num), 
                                    "", xfun::sans_ext(x)), 1L, fig.num)
  }
  else {
    if (nzchar(size)) 
      size = sprintf("[%s]", size)
    res = sprintf("\\includegraphics%s{%s} ", size, if (getOption("knitr.include_graphics.ext", 
                                                                  FALSE)) 
      x
      else xfun::sans_ext(x))
    lnk = options$fig.link
    if (is.null(lnk) || is.na(lnk)) 
      res
    else sprintf("\\href{%s}{%s}", lnk, res)
  }, resize2, sub2, sep.cur, align2, fig2)
}

knitr::knit_hooks$set(plot = appendcaption)
```

```{r, warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  cache.path = "../cache/",
  cache.extra = 3,
  dpi = 300
)

library(metR)
library(data.table)
library(ggplot2)
library(magrittr)
library(ggperiodic)
library(asymsam)
library(latex2exp)

@@

```{r}
my_spectrum <- function(data, spans = NULL, R = 1000, ..., probs = 0.95) {
  mtm <- spec.pgram(data, spans = spans, ..., plot = FALSE)

  out <- as.data.table(mtm[c("freq", "spec")])

  out[, boot_null := null_spec(data, spans = spans, R = R, ..., probs = probs)]

  return(out[])
}

null_spec <- memoise::memoise(function(data, spans, R = 1000, ..., probs = 0.95) {

  b <- boot::boot(data, function(d, i) spec.pgram(d[i], spans = spans, 
                                                  ...,
                                                  plot = FALSE)$spec, 
                  R = R)

  apply(b$t, 2, quantile, probs = probs)
})

indexes %>% 
  copy() %>% 
  # .[, estimate_norm := estimate_norm/sd(estimate_norm), by = .(lev, term)] %>% 
  .[, my_spectrum(estimate_norm, 5), by = .(term, lev)] -> spec
```

```{r A2, fig.cap = "Foutier spectrum", appendix = TRUE}
spec %>%
  .[lev %in% c(30, 700)] %>% 
  ggplot(aes(1/freq/12, spec)) +
  # geom_ribbon(aes(group = interaction(term, rleid(sign(spec - boot_null))), 
  #                 fill = sign(spec - boot_null),
  #                 ymin = spec, ymax = boot_null)) +
    geom_line(aes(color = term)) +
  geom_line(aes(color = term, y = boot_null)) +
  annotation_logticks(sides = "b") +
  scale_color_brewer(palette = "Set1") +
  scale_fill_divergent() +
  scale_x_log10() +
  facet_grid(lev ~ .,labeller = labeller(lev = lev.lab))
```

```{r A3, fig.cap = "Trends for each index at each level. Shading indicates the 95\\% confidence interval.", fig.width = 3, fig.height=3.5, appendix = TRUE}
indexes %>%
  copy() %>% 
  .[, estimate_norm := estimate_norm/sd(estimate_norm), by = .(lev, term)] %>%
  .[, FitLm(estimate_norm, time, se = TRUE), by = .(lev, type = term)] %>% 
  rm_intercept() %>% 
  .[, term := NULL] %>% 
  .[, estimate := estimate*3600*24*365*10] %>% 
  .[, std.error := std.error*3600*24*365*10] %>% 
  setnames("type", "term") %>% 
  ggplot(aes(lev, estimate)) +
  geom_ribbon(aes(ymax = estimate + std.error*1.96, ymin = estimate - std.error*1.96, fill = term), alpha = 0.3) +
  geom_line(aes(color = term)) + 
  geom_hline(yintercept = 0) +
  scale_x_level() +
  coord_flip() 
```

>>>>

```{r setup, echo = FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.path = "",
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	cache.extra = 3,
	cache.path = "../cache/",
	collapse = TRUE,
	comment = "#>",
	dpi = 300,
	out.extra = ""
)
library(metR)
library(data.table)
library(ggplot2)
library(magrittr)
library(ggperiodic)
library(asymsam)
library(latex2exp)

@@

```{r compute-spectrums}
indexes %>% 
  .[lev %in% c(30, 700)] %>% 
  # .[, estimate_norm := estimate_norm/sd(estimate_norm), by = .(lev, term)] %>% 
  .[, fftspectrum(estimate_norm, 5, B = 5000), by = .(term, lev)] -> spec
```

```{r A2, fig.cap = "Fourier spectrum of each timeseries. The shading indicates de 95\\% qunatile derived fitting an AR process and bootstrapping 5000 simulated samples.", appendix = TRUE}
spec %>%
  ggplot(aes(1/freq/12, spec)) +
  geom_area(aes(fill = term, y = ar_spectrum_upp), position = "dodge", alpha = 0.2) +
  # geom_line(aes(color = term, y = ar_spectrum), alpha = 0.5) +
  geom_line(aes(color = term)) +
  annotation_logticks(sides = "b") +
  scale_color_brewer(NULL, palette = "Set1", aesthetics = c("color", "fill")) +
  scale_x_log10("Period (years)") +
  facet_grid(term ~ lev,labeller = labeller(lev = lev.lab, term = lab_sam))
```

```{r A3, fig.cap = "Autocorrelation functions of each timeseries", appendix = TRUE}
acf_dt <- function(...) {
  a <- acf(..., plot = FALSE)
  list(acf = as.vector(a$acf),
       lag = as.vector(a$lag))
}
indexes %>% 
  .[lev %in% c(30, 700)] %>% 
  .[, acf_dt(estimate_norm), by = .(lev, term)] %>% 
  ggplot(aes(lag, acf)) +
  geom_col(aes(fill = term)) +
  scale_fill_brewer(palette = "Set1") +
  facet_grid(term ~ lev,labeller = labeller(lev = lev.lab, term = lab_sam))
```

```{r A4, fig.cap = "Trends for each index at each level. Shading indicates the 95\\% confidence interval.", fig.width = 3, fig.height=5, appendix = TRUE}
indexes %>%
  copy() %>% 
  .[, estimate_norm := estimate_norm/sd(estimate_norm), by = .(lev, term)] %>%
  .[, FitLm(estimate_norm, time, se = TRUE), by = .(lev, type = term)] %>% 
  rm_intercept() %>% 
  .[, term := NULL] %>% 
  .[, estimate := estimate*3600*24*365*10] %>% 
  .[, std.error := std.error*3600*24*365*10] %>% 
  setnames("type", "term") %>% 
  ggplot(aes(lev, estimate)) +
  geom_ribbon(aes(ymax = estimate + std.error*1.96, ymin = estimate - std.error*1.96, fill = term), alpha = 0.3) +
  geom_line(aes(color = term)) +
  scale_fill_brewer(palette = "Set1", aesthetics = c("color", "fill")) +
  geom_hline(yintercept = 0) +
  scale_x_level() +
  coord_flip() +
  facet_grid(term ~ .,labeller = labeller(term = lab_sam))
```

### 2020-07-08 analysis/paper/paper.tex
spectrum

\begin{figure}
\includegraphics{A2-1} \appendcaption{A2}{Foutier spectrum}\label{fig:A2}
\end{figure}

\begin{figure}
\includegraphics{A3-1} \appendcaption{A3}{Trends for each index at each level. Shading indicates the 95\% confidence interval.}\label{fig:A3}
\end{figure}

>>>>

\begin{figure}
\includegraphics{A2-1} \appendcaption{A2}{Fourier spectrum of each timeseries. The shading indicates de 95\% qunatile derived fitting an AR process and bootstrapping 5000 simulated samples.}\label{fig:A2}
\end{figure}

\begin{figure}
\includegraphics{A3-1} \appendcaption{A3}{Autocorrelation functions of each timeseries}\label{fig:A3}
\end{figure}

\begin{figure}
\includegraphics{A4-1} \appendcaption{A4}{Trends for each index at each level. Shading indicates the 95\% confidence interval.}\label{fig:A4}
\end{figure}
